---
title: "LA1_EDA"
author: "samprita(1NT20IS143),Smiti G kalmady(1NT20IS163)"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
  pdf_document: default
---
#Loading the dataset
```{r}
credit_card<-read.csv("creditcard.csv")
```
#head of the data
```{r}
head(credit_card)
```
#tail of the dataset 
```{r}
tail(credit_card)
```
#assigning to the variable
```{r}
amount<-credit_card$Amount
```
#sum of the dataset
```{r}
sum(amount)
```
#mean of the dataset
```{r}
mean(amount)
```
#variance of the dataset
```{r}
var(amount)
```
#standard deviation of the dataset
```{r}
sd(amount)
```
#median of the dataset
```{r}
median(amount)
```
#median absolute deviation
```{r}
mad(amount)
```
#listing the files of dataset
```{r}
ls()
```
#min and max of dataset
```{r}
min(credit_card$Amount)
max(credit_card$Amount)
```


#structure of data set
```{r}
str(credit_card)
```

#Calculate the total number of rows in the dataset
```{r}
summary(credit_card)
```
#Calculate the total number of rows in the dataset:
```{r}
nrow(credit_card)
```
#Calculate the total number of columns in the dataset:
```{r}
ncol(credit_card)
```
#Filter the dataset to include only rows that meet a certain condition:
```{r}
filtered_data <- credit_card[credit_card$Amount > 100, ]
print(filtered_data)

```
#Sort the dataset based on a specific column:
```{r}
sorted_data <- credit_card[order(credit_card$Amount), ]
print(sorted_data)
```

#Count the number of occurrences of unique values in a specific column:
```{r}
table(credit_card$Amount)
```
#Calculate the percentage of missing values in each column:
```{r}
colMeans(is.na(credit_card)) * 100
```

#Convert a column to a factor with custom levels:
```{r}
credit_card$Amount <- factor(credit_card$Amount, levels = c("level1", "level2", "level3"))
```

#Remove duplicate rows:
```{r}
credit_card1 <- unique(credit_card)
print(credit_card1)
```

#Rename a column in the dataset:
```{r}
names(credit_card)[2] <- "v_2"
credit_card$v_2

```
#Create a new column that is the sum of two existing columns:
```{r}
library(dplyr)
new_data <- transmute(credit_card, sum_column = v_2 + V3)
print(new_data)
```
```{r}
arrange(credit_card,V5, V2)
```
#sort the dataset
```{r}
library(dplyr)
sorted_data <- arrange(credit_card, Amount)
print(sorted_data)
```

#matrix of the dataset
 
```{r}
matrix <- matrix(credit_card$V4,nrow=20,ncol=20)
print(matrix)
```
## 37) dataframe creation
 
```{r}
s_vector = credit_card$Amount
t_vector = credit_card$Time
df <- data.frame(col1=credit_card$Time,col2=credit_card$V10)
print(head(df))
```
## checking if factor
```{r}
print(is.factor(credit_card))
```

##viewing only matching package names
 
```{r}
ls(pattern = 'f')
```
##  removing packages
 
```{r}
rm(list = ls(pattern = 'dfa'))
ls()
```

## 55) to view previously executed commands
 
```{r}
#history()
```

## 57) defining a function
```{r}
cool_function <- function(x) {
  x <- x*5
  return(x)
 
}
```

## 58) print object type of function
```{r}
cool_function <- function(x) {
  x <- x*5
  return(x)
}
typeof(cool_function)
```



##Convert Dataframe into matrix
 
```{r}
 
df1 <- data.frame(col1=credit_card$V3,col2=credit_card$V3,col3=credit_card$V4)
 
df2.mat=as.matrix(df1)
 
print(head(df2.mat))
```
#Convert Matrix into dataframe
 
```{r}
cmat= cbind(credit_card$V10,credit_card$V11)
mat2frame=as.data.frame(cmat)
print(head(mat2frame))
```


# dataframe to list
 
```{r}
frame.list=as.list(credit_card$Time)
print(head(frame.list))
```
# converting data frame to stack
```{r}
stackdf <- data.frame(pop=credit_card$Amount,y=credit_card$Time)
stackdf.stack=stack(stackdf)
print(head(stackdf.stack))
 
```

#unstack of a stack
```{r}
unstack(stackdf.stack)
```
 
## saving data files to disk
```{r}
save(list = ls(pattern = 'r'), file = "C:\\Users\\Samprita\\Downloads\\credit card\\edala1.Rmd")
```
## reading data files from disk
```{r}
load(file='edala1.Rmd')
```

 
## finding data on disk
```{r}
dir()
```
 
##pie chart
```{r}
pie(credit_card$Time,credit_card$Amount)
```

#exponential growth
```{r}
df.exp <- exp(df1$col1)
print(head(df.exp))
```
## logrithm
```{r}
df.exp <- log(df1$col1)
print(head(df.exp))
```

## scaling a matrix
```{r}
scale(matrix)
```
## 100)changing row and column values of a matrix
```{r}
print(head(matrix))
mat2 = sweep(x = matrix, MARGIN = 1,STATS = 5, FUN = "+")
print(head(mat2))
```













































